### 2022-06-28 manuscript.tex
Merge pull request #245 from SORTEE-Github-Hackathon/phpb-consistency-use-cases-c [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2574365882

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b78a03a54df81c17eb98b9ca80e842dcb1883ab1/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b78a03a54df81c17eb98b9ca80e842dcb1883ab1}{SORTEE-Github-Hackathon/manuscript@b78a03a}
on June 24, 2022.

@@

Research papers are condensed outputs that hide the underlying intellectual and computational workflows, including the treatment of the raw data and analytical steps.
Granting readers access to code and other documentation of the analysis allows them to retrace and comprehend analytical decisions.
GitHub provides a platform to access all aspects of the project, and can be linked to platforms that create citable DOIs, rather than just the final manuscript.
While often thought of as storage for data and code, GitHub repositories can also be used to publish a time-stamped preregistration of research plans and hypotheses.

Conventional research practices typically rely on one or two people running and checking the data analyses, while most coauthors (and readers of the subsequent publication) see only the final results and a verbal description of the analytical steps.
In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{47}}.
Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.

This transparency can similarly be extended beyond coauthors to the entire scientific community.
Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{48}}.
Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
GitHub even provides a useful Discussions Forum (\url{https://docs.github.com/en/discussions}) that aids the direct communication with repository owners, as well as the GitHub Community (\url{https://github.community/}) forum for more general questions and sharing of expertise (\protect\hyperlink{tbl:roles}{Table 1}.

@@

The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{49}}.
Often with these types of short-term research projects, once the contract expires, the research code upkeep tends to fall off as the researchers move on to new projects.
Additionally, if the code is kept on only the researcher's personal devices, it becomes increasingly difficult to access the code for future uses.
As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{49}}.

GitHub facilitates project continuity among research code by providing tools that make this handover period easier.
As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{50}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}}.
There are also multiple means by which to archive code dependency information with GitHub.
Dependencies can be described in README files, added to environment.yml and/or an environment.txt file, or stored in a repository using tools such as renv (\url{https://rstudio.github.io/renv/articles/renv.html}).
This ensures that as packages continue to develop with new syntax, code will still run as it did when it was developed.

Within EEB projects, tasks are often divided among contributors taking various roles (see CRediT taxonomy, \url{https://casrai.org/credit/}).
The creation of project repositories is commonly the purview of those involved in the code, formal analysis, and/or visualization components of the project through their roles as code writers.
However, the structural components of a typical GitHub repository and the derived EEB-specific templates can provide functional ways for other collaborators not contributing to code to be engaged in aspects of repository design in a way that improves institutional memory and facilitates project continuity.
These other collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
In (Figure \ref{fig:scatterblob}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.

@@

GitHub Organizations offer a shared virtual space that allows a team to work in different repositories, while remaining tied together under a larger figurehead, such as a laboratory, a department, an organization, or a large project involving several teams.
Organizations are well-suited to ensure larger projects with many steps or moving parts are constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on any one individual.
Because the repositories are grouped in one virtual space, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.

Contributors can be assembled into teams within an organization, which allows administrators to assign roles and tasks to groups of people.
Whereas access to repositories is usually assigned to individual contributors, Organizations facilitate the management of access permissions by allowing each team to be granted access to certain repositories, and not to others.
This ensures that more sensitive repositories remain as restricted as needed, while repositories with greater general interest can be easily accessible to many members at once.

As an example, GitHub Organizations are particularly well-suited to house documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other such documents that evolve collaboratively over time and are relevant to many colleagues.
In this way, teams can have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or lost their copies of project data.
This application extends to research centres, which may include several distinct projects that remain linked under a given institution, such as the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}).
Of course, the utility of this tool goes beyond laboratories - they are useful to structure the organization, presentation, and outcomes of working groups such as the hackathon which inspired this paper (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) by keeping track of all materials as ideas develop and take shape in one virtual space.
Organizations are also convenient for hosting a set of related learning materials such as a set of lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be updated by an ever-evolving group of contributors over time.

Using GitHub organizations as a research group or even for a handful of individuals working on a group of projects can be incredibly useful for all involved.
GitHub organizations are relatively easy to set up, and especially easy to manage as membership to the organization changes through time.
Not only is it a useful way to store repositories of lab-related research products, but it is also incredibly helpful for storing ``living documents'' that may be edited frequently, and may be linked to a lab website (that could also be generated via a repository that lives within the organization).
The use of the ``Teams'' feature can allow certain groups to have varying levels of access to repositories in the organization with a select group having push access to some repositories but not others.
This can manifest in a group working on some common dataset(s) to have push access to the handful of repositories used for processing sequence data, while another group of students/researchers may have push access to an entirely different set of repositories.
The organization structure also allows for easy tracking of issues, projects, and discussions related to the research group, and provides group leads an easy birds-eye view of the progress going on across multiple projects.

@@

There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{51}}.
This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
Until now, resources and practical guidance specifically focused on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2} Box\textsuperscript{\protect\hyperlink{ref-box:tips}{\textbf{box:tips?}}}).
We felt these resources have been extremely useful for us to learn to use GitHub in our own work, and that a collation of the main ideas into one medium, while adding on our personal perspectives, would be of use to the EEB community.

@@

A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues.
The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{52}}) allows data to be stored away from GitHub and linked dynamically.
We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
10 Tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{53}} and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub. \\
4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com}).} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax}).} so that you can write clear metadata README files for your repositories. \\
6. \textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{54}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{55}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}. \\
7. \textbf{Don't be afraid of trial and error.} One of the best ways to learn GitHub is the trial and error method. Learning from your own mistakes can be the better way to master your GitHub abilities. In any case, GitHub has the advantage of making it easy to go back to any steps that you desire via version controlling if you make mistakes. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course Rmarkdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}) \\
9. \textbf{Try to begin committing with GUI (Graphical user interface) tools.} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features. \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
\CSLLeftMargin{47. }
\CSLRightInline{January 18, P. L. B. K. \& Pm, 2022. 2:51. \#PruittData and the Ethics of Data in Science. \emph{Ecology for the Masses} \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/} (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
\CSLLeftMargin{48. }
\CSLRightInline{Culina, A., van den Berg, I., Evans, S. \& Sánchez-Tójar, A. \href{https://doi.org/10.1371/journal.pbio.3000763}{Low availability of code in ecology: A~call for urgent action}. \emph{PLoS Biol} \textbf{18}, e3000763 (2020).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\CSLLeftMargin{50. }
\CSLRightInline{About code owners. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}.}

\leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
\CSLLeftMargin{51. }
\CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\CSLLeftMargin{52. }
\CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}

\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
\CSLLeftMargin{53. }
\CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. (2019) doi:\href{https://doi.org/10.5281/zenodo.3264950}{10.5281/zenodo.3264950}.}

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
\CSLLeftMargin{54. }
\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
\CSLLeftMargin{55. }
\CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab}{SORTEE-Github-Hackathon/manuscript@773da7b}
on June 28, 2022.

@@

Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{47}}.
In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.

Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
GitHub can serve as a tool for open and tractable research development.
Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{48}}).
Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.

This transparency can be extended beyond coauthors to the entire scientific community and to the public.
Supplying code for (novel) methods that are proposed or used reduces barriers to knowledge, improving the ability of others to build on existing work.
This results in greater proliferation and accessibility for a broader audience.
Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
Moreover, researches can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from other researchers in ecology and evolution on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 1}.

@@

Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{49}}.
Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
Additionally, code and data can be difficult to access when kept only on the personal devices of researchers\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{50}}.

GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},see \protect\hyperlink{ref-D4C4k4ak}{49}}.
Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{51}}), who can also can change through time allowing for the transition of code from one cohort of researchers to the next.
Other project collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.

GitHub also allows users to describe and store information about software and code dependencies, ensuring that code can run using the same version of software as when it was initially developed.
This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the usage of actions with specific software versions in its automation tool, GitHub Actions.

@@

GitHub Organizations are shared virtual spaces that allow teams to work in different repositories, while remaining tied together under a larger group, such as a laboratory, department, or project involving several teams.
Organizations are well-suited to ensure larger projects with many steps or moving parts are constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on any one individual.
Because the repositories are grouped, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.

Contributors can be assembled into teams within an organization, which allows administrators to assign roles, tasks, and repository modification permissions to organization members.
Whereas access to repositories is usually assigned to individual contributors, Organizations facilitate the management of access permissions by allowing teams to be granted access to specific repositories.
This ensures repositories with sensitive information remain as restricted as needed, while repositories with general stay easily accessible to selected member groups.
The organization structure also allows for easy issue tracking and discussions related to research content and progress.

As an example, GitHub Organizations are particularly well-suited to house documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other such documents that evolve collaboratively over time and are relevant to many colleagues.
In this way, teams can have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or lost their copies of project data.
This application extends to research centres, which may include several distinct projects that remain linked to institutions, such as the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}).
The team organizing the hackathon which inspired this paper used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to keeping track of all materials as ideas developed and took shape in one virtual space.
Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be updated by an ever-evolving group of contributors over time.

@@

There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{52}}.
This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
Until now, resources and practical guidance specifically focused on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2} Box\textsuperscript{\protect\hyperlink{ref-box:tips}{\textbf{box:tips?}}}).
We felt these resources have been extremely useful for us to learn to use GitHub in our own work, and that a collation of the main ideas into one medium, while adding on our personal perspectives, would be of use to the EEB community.

@@

A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues.
The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{53}}) allows data to be stored away from GitHub and linked dynamically.
We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
10 Tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{54}} and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub. \\
4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com}).} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax}).} so that you can write clear metadata README files for your repositories. \\
6. \textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{55}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{56}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}. \\
7. \textbf{Don't be afraid of trial and error.} One of the best ways to learn GitHub is the trial and error method. Learning from your own mistakes can be the better way to master your GitHub abilities. In any case, GitHub has the advantage of making it easy to go back to any steps that you desire via version controlling if you make mistakes. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course Rmarkdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}) \\
9. \textbf{Try to begin committing with GUI (Graphical user interface) tools.} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features. \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
\CSLLeftMargin{47. }
\CSLRightInline{Culina, A., van den Berg, I., Evans, S. \& Sánchez-Tójar, A. \href{https://doi.org/10.1371/journal.pbio.3000763}{Low availability of code in ecology: A~call for urgent action}. \emph{PLoS Biol} \textbf{18}, e3000763 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
\CSLLeftMargin{48. }
\CSLRightInline{January 18, P. L. B. K. \& Pm, 2022. 2:51. \#PruittData and the Ethics of Data in Science. \emph{Ecology for the Masses} \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/} (2020).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
\CSLLeftMargin{50. }
\CSLRightInline{Vines, Timothy~H. \emph{et al.} \href{https://doi.org/10.1016/j.cub.2013.11.014}{The Availability of Research Data Declines Rapidly with Article Age}. \emph{Current Biology} \textbf{24}, 94--97 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\CSLLeftMargin{51. }
\CSLRightInline{About code owners. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}.}

\leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
\CSLLeftMargin{52. }
\CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\CSLLeftMargin{53. }
\CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}

\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
\CSLLeftMargin{54. }
\CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. (2019) doi:\href{https://doi.org/10.5281/zenodo.3264950}{10.5281/zenodo.3264950}.}

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
\CSLLeftMargin{55. }
\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
\CSLLeftMargin{56. }
\CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}
